Response to reviewers

### 2022-05-12 paper/paper-jsdse/paper-jsdse.tex
removed DONE from response

The challenging part of detecting an anomaly using the robustness weight is determining the weight threshold beyond which the observations are considered outliers. It is also important not to be too aggressive in outlier removal, because this would overly smooth the data, and ignore actual workforce experiences important wage volatility such as, abnormally high wages for a fleeting amount of time. To explore the risk of being overly vigorous in labeling observations as outliers, a range of threshold value were assessed. Numerous samples of individuals were drawn for each threshold, and the smoothness of the profiles was examined. Overly smooth profiles would indicate the replacement of values was too severe, resulting in the removing the very interesting volatility of wages seen in many individuals. This was achieved using a purpose written \texttt{shiny} (Chang et al. 2020) app (provided with the code of this paper). Observations where a change was made are tracked with a new variable called \texttt{is\_pred}, so that this effect in the downstream analyses can be monitored.

@@

The original set, containing wages of high school dropouts (Singer and Willett 2003) from 1979 through to 1994, is available in the R package \texttt{brolgar}. To compare the refreshed data with the original, we need to subset the data into a matching cohort of high school dropouts. There are multiple ways to match a comparative cohort from the updated data -- the simplest approach is to subset to individuals with matching IDs in the original data and restricting the longitudinal measurements to the same years; another approach is to replicate the process as suggested by the description of the original data thus identifying a new (and possibly removal of old) set of individuals that is included in the refreshed data. We use the latter approach and as the first step we identify individuals who dropped out of high school.

@@

\begin{itemize}
\item
  \textbf{Codes}: R script to reproduce data tidying and cleaning is available at \url{https://numbats.github.io/yowie/articles/process-data.html}. The code for the extreme value handling with robust linear fits is in \url{https://numbats.github.io/yowie/articles/input-to-valid-data.html}.
\item
  \textbf{R Package}:\texttt{yowie} is a data container R package that contains 3 datasets, namely the high school mean hourly wage data, high school dropouts mean hourly wage data, and demographic data of the NLSY79 cohort. This package can be accessed from \url{https://github.com/numbats/yowie}.
\item
  \textbf{shiny app}: An interactive \texttt{shiny} web app to visualise the effect of selecting different weight threshold for substituting the wages data to its predicted value from a fit of the robust linear regression model. This app can be accessed at \url{https://ebsmonash.shinyapps.io/yowie_app/} with the source code provided \url{https://github.com/numbats/yowie/tree/master/app}.
\end{itemize}

>>>>

The challenging part of detecting an anomaly using the robustness weight is determining the weight threshold beyond which the observations are considered outliers. It is also important not to be too aggressive in outlier removal, because this would overly smooth the data, and ignore actual workforce experiences important wage volatility such as, abnormally high wages for a fleeting amount of time. To explore the risk of being overly vigorous in labeling observations as outliers, a range of threshold value were assessed. Numerous samples of individuals were drawn for each threshold, and the smoothness of the profiles was examined. Overly smooth profiles would indicate the replacement of values was too severe, resulting in removing the very interesting volatility of wages seen in many individuals. This was achieved using a purpose written \texttt{shiny} (Chang et al. 2020) app (provided with the code of this paper). Observations where a change was made are tracked with a new variable called \texttt{is\_pred}, so that this effect in the downstream analyses can be monitored.

@@

The original set, containing wages of high school dropouts (Singer and Willett 2003) from 1979 through to 1994, is available in the R package \texttt{brolgar} (Tierney, Cook, and Prvan 2020). To compare the refreshed data with the original, a subset needs to be matched. There are numerous ways to do this, with the simplest being to extract the individuals based on their id being part of the original data and restricting the longitudinal measurements to the same years. However, we decided to try to replicate the process, as suggested by the description of the original data. This requires first identifying individuals who dropped out of high school.

@@

\begin{itemize}
\item
  \textbf{Code}: R script to reproduce data tidying and cleaning is available at \url{https://numbats.github.io/yowie/articles/process-data.html}. The code for the extreme value handling with robust linear fits is in \url{https://numbats.github.io/yowie/articles/input-to-valid-data.html}.
\item
  \textbf{R Package}: \texttt{yowie} is an R data package that contains 3 datasets, namely the high school mean hourly wage data, high school dropouts mean hourly wage data, and demographic data of the NLSY79 cohort. This package can be accessed from \url{https://github.com/numbats/yowie}.
\item
  \textbf{shiny app}: An interactive \texttt{shiny} web app to visualise the effect of selecting different weight threshold for substituting the wages data to its predicted value from a fit of the robust linear regression model. This app can be accessed at \url{https://ebsmonash.shinyapps.io/yowie_app/} with the source code provided \url{https://github.com/numbats/yowie/tree/master/app}.
\end{itemize}

### 2022-05-12 response/response2.Rmd
removed DONE from response

* It is not clear how to handle this. We interpret the comment from the Editor, that the paper is consistent with the call for the special issue. The AE would like it to be clearly one of three types. The paper does have of each of the three types, which we believe has value. There is some wording in the introduction ("An example of this is the wages data made public by Singer and Willett (2003) in their book, “Applied lon- gitudinal data analysis,” which can be used to teach generalized linear models, in addition to hierarchical, mixed effects, and multilevel models.") and we have added additional text in Section 5 Summary, on lessons learned, to help the reader understand the elements that might be used for their teaching. XXX DONE

@@

* We have revised the language, made a note for educators on usage, and referred to the SAGER guidelines. XXX DONE

@@

* We have added more explanation of the two variables, and suggestions of where to use one and the other in classroom analyses. XXX DONE

@@

* Using `rlm` with the `nest` and `map` functions from `tidyr`, efficiently and simply fit these models. They can be easily explained in a classroom setting, and equip students generally with advanced data handling skills. Similar results would be obtained from using robustlmm, though. We have removed reference to memory and convergence issues. We have also removed a specific reference to threshold used. Having the particular number used is not important for the explanation of the approach and as we have seen from the review, is distracting for the reader. This section has been modified so that the approach is more understandable. XXX DONE

@@

* This is more of a comment than a request to make a change, but we agree that this is an area that could be a good classroom discussion. We have revised the section on handling extremes to make our explanation simpler, with links to the shiny app that we put together to assist in the judgment and choice of threshold. We hope that this provides fodder for discussion. It could definitely be worked into a teaching exercise. XXX DONE

@@

* We have revised the language, referenced the Federal standard, and explained the reasoning for using a single variable.  XXX DONE

@@

* We have revised the introduction to fix this. XXX DONE

@@

* We have added additional bullet points on the benefit for educators in Section 5, in response to the overview comments by the Editor and AE (top of this response). We think it is best to keep content on cleaning and tidying the data, in a reproducible manner, to match the mission of the special issue. XXX DONE

@@

* We have changed all to "refresh" as it is not correct if we say it as a replication because we did not use the exactly same variable and same result (esepcially ID included in the dropouts cohort.) XXX DONE

@@

* See response above to the associate editor, about this concern. XXX DONE

@@

* We have modified the discussion around HRP to be more concise about what we have done with the variable. On page 9, we use the HRP to demonstrate the untidy form of the data. Hence, the sentence “HRP1 1980 and HRP2 1980, contain the information about the job number up to 5...” has been removed. In another part of the manuscript, we explain that if a respondent has multiple jobs, the `mean_hourly_wage` is computed as a weighted average of the hourly wage (`HRP`) for each job with the number of hours worked for each job as weights (provided that the information on the number of hours is available); if the number of hours worked for any job is missing, then the `mean_hourly_wage` is computed as a simple average of all available hourly wages. We hope that our modification makes the manuscript clearer. XXX DONE

@@

* The tables show the number by characteristics (age, sex, and race) in the input data (referring the term in the de Jonge and van der Loo's statistical value chain), i.e., the data we have extracted and tidied from the database. We are not saying it as a clean data as we have not treat the extreme values. We have modified the tables' caption to make this clearer. XXX DONE

@@

* This sentence means that when the revised `hgc` variable were not reported, we only use the unrevised version of the `hgc` in that year. We thank the reviewer for this notice. We agree that this sentences is not clear, so we have modified it. XXX DONE

@@

* We have put the capitalisation back in. Besides, we did not use the term "White" in the dataset as we used the same term reported in the database, which is "Non-Black, Non-Hispanic". XXX Done

>>>>

* It is not clear how to handle this. We interpret the comment from the Editor, that the paper is consistent with the call for the special issue. The AE would like it to be clearly one of three types. The paper does have of each of the three types, which we believe has value. There is some wording in the introduction ("An example of this is the wages data made public by Singer and Willett (2003) in their book, “Applied lon- gitudinal data analysis,” which can be used to teach generalized linear models, in addition to hierarchical, mixed effects, and multilevel models.") and we have added additional text in Section 5 Summary, on lessons learned, to help the reader understand the elements that might be used for their teaching.

@@

* We have revised the language, made a note for educators on usage, and referred to the SAGER guidelines.

@@

* We have added more explanation of the two variables, and suggestions of where to use one and the other in classroom analyses.

@@

* Using `rlm` with the `nest` and `map` functions from `tidyr`, efficiently and simply fit these models. They can be easily explained in a classroom setting, and equip students generally with advanced data handling skills. Similar results would be obtained from using robustlmm, though. We have removed reference to memory and convergence issues. We have also removed a specific reference to threshold used. Having the particular number used is not important for the explanation of the approach and as we have seen from the review, is distracting for the reader. This section has been modified so that the approach is more understandable.

@@

* This is more of a comment than a request to make a change, but we agree that this is an area that could be a good classroom discussion. We have revised the section on handling extremes to make our explanation simpler, with links to the shiny app that we put together to assist in the judgment and choice of threshold. We hope that this provides fodder for discussion. It could definitely be worked into a teaching exercise.

@@

* We have revised the language, referenced the Federal standard, and explained the reasoning for using a single variable.

@@

* We have revised the introduction to fix this.

@@

* We have added additional bullet points on the benefit for educators in Section 5, in response to the overview comments by the Editor and AE (top of this response). We think it is best to keep content on cleaning and tidying the data, in a reproducible manner, to match the mission of the special issue.

@@

* We have changed all to "refresh" as it is not correct if we say it as a replication because we did not use the exactly same variable and same result (esepcially ID included in the dropouts cohort.)

@@

* See response above to the associate editor, about this concern.

@@

* We have modified the discussion around HRP to be more concise about what we have done with the variable. On page 9, we use the HRP to demonstrate the untidy form of the data. Hence, the sentence “HRP1 1980 and HRP2 1980, contain the information about the job number up to 5...” has been removed. In another part of the manuscript, we explain that if a respondent has multiple jobs, the `mean_hourly_wage` is computed as a weighted average of the hourly wage (`HRP`) for each job with the number of hours worked for each job as weights (provided that the information on the number of hours is available); if the number of hours worked for any job is missing, then the `mean_hourly_wage` is computed as a simple average of all available hourly wages. We hope that our modification makes the manuscript clearer.

@@

* The tables show the number by characteristics (age, sex, and race) in the input data (referring the term in the de Jonge and van der Loo's statistical value chain), i.e., the data we have extracted and tidied from the database. We are not saying it as a clean data as we have not treat the extreme values. We have modified the tables' caption to make this clearer.

@@

* This sentence means that when the revised `hgc` variable were not reported, we only use the unrevised version of the `hgc` in that year. We thank the reviewer for this notice. We agree that this sentences is not clear, so we have modified it.

@@

* We have put the capitalisation back in. Besides, we did not use the term "White" in the dataset as we used the same term reported in the database, which is "Non-Black, Non-Hispanic".
